Stack Safety as a Security Property

### 2020-07-09 main.tex
Submit draft

In summary, we offer the following contributions:\bcp{I would still like to
  see these points phrased in ``contribution normal form'': say exactly what
  we did for each one (it's a bit vague---''considers,'' etc.), and
  explicitly say why it is (a) useful, (b) challenging, and (c) novel.}
\begin{itemize}
\item
  % \leo{More? Extensional}\bcp{We might need to invent a word for   this---''quasi-extensional''?}
  A novel formal stack safety property capturing the
  intuitive concepts of strict local state encapsulation and well-bracketed
  control flow~(\cref{sec:lse-and-wbcf}) in terms of security concepts.
  % These properties   rule out common examples of stack memory abuse.
  This property is enforced by 
  the Depth Isolation policy of \citet{DBLP:conf/sp/RoesslerD18}, based on hardware tags~(\cref{sec:conservative}).
\item
  A lockstep stack safety property that is also enforced by the Depth Isolation policy,
  and is more efficient to test, which we prove (in Coq) is stronger than the basic property(~\cref{sec:lockstep}).
\item
  A novel lazy stack safety property that is enforced by the more efficient
  Lazy Tagging and Clearing policy
  of \citet{DBLP:conf/sp/RoesslerD18}, which we prove (in Coq) is weaker than the basic property~(\cref{sec:lazy}).
%  This policy does not enforce our strict
%  local state encapsulation property,
%  but a modified version of it using unique per-activation tags enforces
%  an (also provably) weaker lazy variant of the property, which still prohibits
%  the same intuitively stack unsafe behaviors.
%
% \apt{Awkward, but the truth I fear.} \bcp{I agree the phrasing is awkward,
%   but the point we can make is still strong: To make the property easier
%   to enforce, we can slightly weaken its guarantees; the weaker version is
%   a bit more complicated to state but still retains the pragmatic
%%   protections of the original.}\apt{To clarify: Nick's LT\&C policy uses
%   depth-based tags, which do not enforce even our lazy policy. So we need to
%   introduce a version of LT\&C that uses unique activation tags.}

@@

\leo{Needs high level signposting, transitions}

@@

\theorem
Lockstep stack safety implies stack safety.

\proof
By coinduction on trace lockstep stack safety.
\leo{3000 lines Coq?}
\leo{I can write a TON about this proof, but I'm not sure how much is interesting/how much space we have}.

@@

      \theorem Stack safety implies observable stack safety.

      \proof \leo{TODO: Whatever we say about the previous proof
        we have to say similar things here}

>>>>

In summary, we offer the following contributions:\bcp{I would still like to
  see these points phrased in ``contribution normal form'': say exactly what
  we did for each one (it's a bit vague---''considers,'' etc.), and
  explicitly say why it is (a) useful, (b) challenging, and (c) novel.}
\begin{itemize}
\item
  % \leo{More? Extensional}\bcp{We might need to invent a word for   this---''quasi-extensional''?}
  A novel formal stack safety property capturing the
  intuitive concepts of strict local state encapsulation and well-bracketed
  control flow~(\cref{sec:lse-and-wbcf}) in terms of security concepts.
  % These properties   rule out common examples of stack memory abuse.
  This property is enforced by 
  the Depth Isolation policy of \citet{DBLP:conf/sp/RoesslerD18}, based on hardware tags~(\cref{sec:conservative}).
\item
  A lockstep stack safety property that is also enforced by the Depth Isolation policy,
  and is more efficient to test, which we prove (in Coq) is stronger than the basic property~(\cref{sec:lockstep}).
\item
  A novel lazy stack safety property that is enforced by the more efficient
  Lazy Tagging and Clearing policy
  of \citet{DBLP:conf/sp/RoesslerD18}, which we prove (in Coq) is weaker than the basic property~(\cref{sec:lazy}).
%  This policy does not enforce our strict
%  local state encapsulation property,
%  but a modified version of it using unique per-activation tags enforces
%  an (also provably) weaker lazy variant of the property, which still prohibits
%  the same intuitively stack unsafe behaviors.
%
% \apt{Awkward, but the truth I fear.} \bcp{I agree the phrasing is awkward,
%   but the point we can make is still strong: To make the property easier
%   to enforce, we can slightly weaken its guarantees; the weaker version is
%   a bit more complicated to state but still retains the pragmatic
%%   protections of the original.}\apt{To clarify: Nick's LT\&C policy uses
%   depth-based tags, which do not enforce even our lazy policy. So we need to
%   introduce a version of LT\&C that uses unique activation tags.}

@@

@@

\paragraph*{THEOREM}
Lockstep stack safety implies stack safety.

\paragraph*{PROOF}
By coinduction on trace lockstep stack safety.
\leo{3000 lines Coq?}
\leo{I can write a TON about this proof, but I'm not sure how much is interesting/how much space we have}.

@@

      \paragraph*{THEOREM} Stack safety implies observable stack safety.

%      \paragraph*{PROOF} \leo{TODO: Whatever we say about the previous proof
 %       we have to say similar things here}
